The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-17 dit-paper_ieee.tex
theorem 1

\begin{abstract}
	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
	conditions in the case of small changes in task parameters, such as
	different WCET values when porting a system to a different platform. The \mbox{C-space} describes the set of execution
	times for which a system is feasible, which allows system designers to quickly
	find the best platform for a given task set. This paper extends previous works
	to generalize the description of the C-space for Earliest Deadline First
	scheduling to systems with initial task offsets. The feasibility gain offered
	by offsets is then expressed as the volume ratio between the C-space of an
	asynchronous system and its corresponding synchronous system. The problem
	requires solving multiple similar instances of the Chinese Remainder Problem,
	for which an algorithm efficient in this context is provided.
\end{abstract}

@@

	In Section~\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
	system based on the demand bound function test. Then we show why applying this
	test on the interval starting at $t_d$
	and spanning an hyperperiod is sufficient when $t_d$ exists. A
	numerical example is also given.

@@

	\subsection{Model}
		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period, which is the exact time between two consecutive arrivals.
		The constrained deadline property implies that $D_i \leq T_i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0$ for all tasks) and \emph{asynchronous systems} (which are not synchronous).

@@

		\begin{definition}
			The \textbf{demand-bound function (DBF)}
			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
			equal to the maximum cumulated execution time of jobs of $\tau$ contained in the
			closed interval $[t_1, t_2]$.
		\end{definition}

@@

		A necessary and sufficient condition of feasibility can easily be written
		based on the DBF \cite{baruah1999generalized}

		\begin{theorem}
			\begin{equation}
				\begin{array}{c}
					\{\tau_1, ..., \tau_n\} \: \text{is feasible}  \iff \\
					\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
				\end{array}
			\end{equation}
		\end{theorem}

	\subsection{C-space of synchronous systems}
	\label{sct:cspaceDescr}

@@

		The DBF test gives us a list of inequations on the WCET values of the task set
		which, taken together, are a necessary and sufficient condition of feasibility. They
		can all be written in the following way:
		\begin{equation}
			\sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{equation}
		Note that for given values  of $(t_1, t_2)$, the $n_i(t_1, t_2)$ are
		constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.

>>>>

\begin{abstract}
	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
	conditions in the case of small changes in task parameters, such as
	different WCET values when porting a system to a different platform. The C-space describes the set of execution
	times for which a system is feasible, which allows system designers to quickly
	find the best platform for a given task set. This paper extends previous works
	to generalize the description of the C-space for Earliest Deadline First
	scheduling to systems with initial task offsets. The feasibility gain offered
	by offsets is then expressed as the volume ratio between the C-space of an
	asynchronous system and its corresponding synchronous system. The problem
	requires solving multiple similar instances of the Chinese Remainder Problem,
	for which an algorithm efficient in this context is provided.
\end{abstract}

@@

	In Section~\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
	system based on the demand bound function test. Then we show why applying this
	test on the interval starting at $t_d$
	and spanning an hyperperiod when $t_d$ exists is sufficient. A
	numerical example is also given.

@@

	\subsection{Model}
		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
		The constrained deadline property implies that $\forall i,\; D_i \leq T_i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).

@@

		\begin{definition}
			The \textbf{demand-bound function (DBF)}
			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
			equal to the maximal cumulated execution time of jobs of $\tau$ contained in the
			closed interval $[t_1, t_2]$.
		\end{definition}

@@

		A necessary and sufficient condition of feasibility can easily be written
		based on the DBF \cite{baruah1999generalized}
		\begin{theorem} 
			\begin{equation*}
				\begin{array}{c}
					\{\tau_1, ..., \tau_n\} \: \text{is feasible}  \iff \\
					\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall t_1,t_2 \; s.t. \; 0 \leq t_1 \leq t_2
				\end{array}
			\end{equation*} 
		\end{theorem}
	\subsection{C-space of synchronous systems}
	\label{sct:cspaceDescr}

@@

		The DBF test gives us a list of inequations on the WCET values of the task set
		which together are a necessary and sufficient condition of feasibility. They
		can all be written in the following way:
		\begin{equation}
			\sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{equation}
		Note that for a given $t$, we have that the $n_i(t)$ are
		constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.
